---
title: "basketball_data_code"
author: "Austin Chen"
date: "8/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(xml2)
library(rvest)
library(tidyverse)
library(ggplot2)
library(corrplot)
```
## Reading CSV File
Must be in same directory as project
```{r}
bball_data = read.csv("players_stats_by_season_full_details.csv")
```




## Basic R functions
```{r}
head(bball_data)
```

```{r}
tail(bball_data)
```
```{r}
summary(bball_data)
```

```{r}
# View(bball_data)
```

## Editing the Dataset
```{r}
bball_data$three_point_pct = round((bball_data$X3PM / bball_data$X3PA), digits = 2)
```

```{r}
bball_data$MIN_per_G = round((bball_data$MIN / bball_data$GP), digits = 2)
```

```{r}
bball_data$TOV_per_G = round((bball_data$TOV / bball_data$GP), digits = 2)
```


```{r}
bball_data$fg_pct = round((bball_data$FGM / bball_data$FGA), digits = 2)
```

```{r}
bball_data$ft_pct = round((bball_data$FTM / bball_data$FTA), digits = 2)
```

```{r}
bball_data$REB_per_G = round((bball_data$REB / bball_data$GP), digits = 2)
```

```{r}
bball_data$assist_per_G = round((bball_data$AST / bball_data$GP), digits = 2)
```

```{r}
bball_data$steals_per_G = round((bball_data$STL / bball_data$GP), digits = 2)
```

```{r}
bball_data$BLK_per_G = round((bball_data$BLK / bball_data$GP), digits = 2)
```

```{r}
bball_data$points_per_G = round((bball_data$PTS / bball_data$GP), digits = 2)
```

# Now we can get rid of the columns we do not need
```{r}
glimpse(bball_data)
```

```{r}
bball_data = bball_data[,-c(7:22)]
```

# We can also create a new dataframe with only the stats and the relevant information
```{r}
glimpse(bball_data)
```


```{r}
bball_stats = bball_data[,c(1:5,16:25)]
```

```{r}
# View(bball_stats)
```

# Now we have created a data frame called "bball_stats" with relevant stats for easy readibility

```{r}
head(bball_data)
```



## Subsetting the data


```{r}
nba = bball_data[bball_data$League == "NBA",]
```

```{r}
summary(bball_data[bball_data$League == "NBA",])
```
# Another way to subset data using the piping operator ( %>% )


```{r}
bball_data %>% 
  filter(League == "NBA")
```


```{r}
summary(bball_data %>% 
  filter(League == "NBA"))
```

## Making visually appealing plots with bball

```{r}
ggplot(bball_data, aes(x = points_per_G)) + geom_density(color = "blue") + ggtitle("Points Per Game Density")
```


```{r}
ggplot(bball_data, aes(x = points_per_G, y = height_cm)) + geom_point(color = "orange") + ggtitle("Relationship between height and points per game")
```

```{r}
ggplot(bball_data, aes(x = REB_per_G, y = height_cm)) + geom_point(color = "green") + ggtitle("Relationship between height and points per game")
```
We can see here that heigh does play somewhat of a role in rebounds, but in points the correalation is not evident. 

```{r}
ggplot(bball_data %>% 
         filter(League == "NBA"), aes(x = fg_pct)) + geom_density(color = "purple") + ggtitle("NBA fg_pct distribution")
```

```{r}
ggplot(bball_data %>% 
         filter(League == "Euroleague"), aes(x = fg_pct)) + geom_density(color = "turquoise") + ggtitle("Euroleague fg_pct distribution")
```
```{r}
ggplot(bball_data %>% 
         filter(League == "NBA"), aes(x = height)) + geom_bar(color = "red") + ggtitle("NBA height Distribution")
```

```{r}
ggplot(bball_data %>% 
         filter(League == "Euroleague"), aes(x = height)) + geom_bar(color = "red") + ggtitle("Euroleague height Distribution")
```
```{r}
ggplot(bball_data, aes(x = height, y = points_per_G, color = League)) + geom_point() + ggtitle("Height vs PPG for all leagues")
```
```{r}
ggplot(bball_data, aes(x = height, y = points_per_G, color = birth_year)) + geom_point() + ggtitle("Height vs PPG for all leagues")
```

```{r}
bball_data %>% 
  filter(points_per_G == max(bball_data$points_per_G))
```
The highest points per game from across all leagues belong to Jonathan Gibson of the CBA.
```{r}
glimpse(bball_data)
```
Here I can use glimpse to easily specify which columns I need. 
```{r}
bball_matrix = as.matrix(bball_stats[ , c(6:15)])
corrplot(cor(bball_matrix, use="pairwise.complete.obs"), is.corr = FALSE, method = "circle", type = "upper")
```

```{r}
bball_matrix = as.matrix(bball_stats[ , c(6:15)])
corrplot(cor(bball_matrix, use="pairwise.complete.obs"), is.corr = FALSE, method = "circle", type = "lower")
```
These plots show the correalation between stats. The bigger and darker the circle is, the more correalted the corresponding statistics are. 

